A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
attempt with log transformation

# campare untransformed variance to transformed variance
summary(PM_dat_D$vi)
summary(PM_dat_D$vi_percent)
PM_dat_D[10:12,]
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvPer <- rma.mv(
   yi = yi_percent,
   V = vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

>>>>

# compare untransformed variance to transformed variance
summary(PM_dat_D$vi)
summary(PM_dat_D$vi_percent)

# scale to 100% 
PM_dat_D$yi_percent  <- PM_dat_D$yi_percent * 100
PM_dat_D$vi_percent  <- PM_dat_D$vi_percent * 100

# scale to 100% 
PM_dat_D$L_yi_p  <- log(PM_dat_D$yi_percent + 1 )
PM_dat_D$L_vi_p  <- log(PM_dat_D$vi_percent +1 )
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvPer <- rma.mv(
   yi = L_yi_p,
   V = L_vi_p,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)
